---
title: "FP_midterm"
Author: "Janette Avelar David Fainstein Joe Swinehart Makayla Whitney"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
#Note: see DA's guidance on caching and clearing the cache as needed. If you run into trouble, clear the Knitr cache from the "Knit" menu above.
```

# Part A
## Task 1
Use the given function to download all of the data from the 2014-15 to 2017-18 school years and bind it into a single data frame, using a single function (i.e., one line of code). Note, this may take a minute or two to run, depending on your Internet speed.

Conduct some basic data cleaning to make your data file look like the following.

* Filter for only student groups coded as "White" or "Hispanic/Latino".
* Select variables related to the number of students in each of the levels (1:4), and not percentages or collapsed levels.
* Remove any row that has missing data in any of the n variables

```{r importing_cleaning}
library(purrr)
library(readr)
library(fs)
library(tidyverse)
library(gapr)

#code from DA
download_file <- function(year) {
  link <- glue::glue("https://www.oregon.gov/ode/educator-resources/assessment/TestResults20{year}/pagr_schools_ela_raceethnicity_{year-1}{year}.xlsx")
  rio::import(link, setclass = "tibble", na = c("-", "--", "*"))
}

#Single-line read-in & staple together data frames
combined <- map_dfr(15:18, ~download_file(.), .id = "file")

#Tidy up combined data frame: focus on number of students, exclude percentages and drop NAs
combined_clean <- combined %>% 
  filter(`Student Group` == "White" | `Student Group` == "Hispanic/Latino") %>% 
  select(`Academic Year`,
         `District`,
         `School`,
         `Student Group`,
         `Grade Level`,
         `Number Level 1`,
         `Number Level 2`,
         `Number Level 3`,
         `Number Level 4`) %>% 
  pivot_longer(cols = starts_with("Number"),
               names_to = "level",
               values_to = "n") %>% 
  mutate(level = gsub("Number Level", "", level)) %>% 
  drop_na()

```

## Task 2

Sum the n across grades and school for each district within each academic year, student group, and level. Calculate the number of schools (unique schools listed) for each district. Also move your data to a wider format where the student groups become new columns, filled by the district n. Remove districts that did not report numbers for one or both student groups (i.e., drop missing data from the new columns).

```{r summing_calculating}
# David will try this section too - kind of a natural follow up to Part 1

  sum_grouped <- combined_clean %>% 
  group_by(`District`) %>% 
  mutate(n_schools = length(unique(`School`))) %>% 
  group_by(`Academic Year`, `District`, `Student Group`, `level`, `n_schools`) %>% 
  summarise(n = sum(n)) %>% 
  pivot_wider(names_from = `Student Group`,
              values_from = "n") %>% 
  drop_na()

sum_grouped_arranged <- sum_grouped [, c(1, 2, 4, 3, 5, 6)]
arrange(sum_grouped_arranged, `District`)



```

# Part 2
## Task 1

Estimate the average achievement differences in terms of an effect size for every school district in the state that reported data on both student groups (i.e., using the data we created above), for each academic year. Conduct this analysis twice, once using group_by() %>% nest() map() and once using nest_by() %>% summarize().

``` {r estimating average diffs}
#ignore the below. This was to raise the API limit
#remotes::install_github("datalorax/gapr")
#remotes::install_github("dpc10ster/RJafroc@662c4bf3bcd725d8fa148a3e7db69168294ae57e")
#Sys.setenv(R_REMOTES_NO_ERRORS_FROM_WARNINGS="true")
#writeLines('PATH="${RTOOLS40_HOME}\\usr\\bin;${PATH}"', con = "~/.Renviron")
#install.packages("remote")
#usethis::create_github_token()
#usethis::edit_r_environ()

# Reference estimate_v() from assignment:
# sum_grouped_arranged[1:4, ] %>% # data source - just first four rows for first district
#   estimate_v("White", "Hispanic/Latino") # columns for reference/focal groups

# Analysis 1
est1 <- sum_grouped_arranged %>% 
  group_by(`Academic Year`, `District`) %>% 
  nest() %>% 
  mutate(est_values = vector("list", length("data"))) %>%
  map(.data$data, ~estimate_v("White", "Hispanic/Latino"))

map_est <- map(, ~estimate_v("White", "Hispanic/Latino"))
         

#wrap in list?
# The example code has d[1:4, ]. This is just to select the first four rows, which is the first district for the first year. The `estimate_v()` function assumes you are feeding it a data frame for one district for one year. You then just give it the columns you want it to estimate the gap from. So in your code, you need to remove the [1:4, ] part, because you’ve already got data for one district by the way that you’ve nested it. You should also be using mutate, and it looks like you’re missing a tilde (~).

  
# Analysis 2
est2 <- sum_grouped_arranged %>% 
  ungroup() %>% 
  nest_by(`Academic Year`, `District`) %>% 
  summarize(estimate_v(.data$data, "White", "Hispanic/Latino"))

```

## Task 2

Reproduce the following plot to confirm that the estimates are equivalent across methods
``` {r reproduce_plot}



````

## Task 3

The plot below shows the achievement difference estimates for one school district across years. Produce a similar plot to the below for each of the first 100 school districts. Once you’ve created all the plots, reproduce them again using an alternative method. Make sure you don’t miss the caption noting the number of schools in the district.

``` {r another_plot_production}
#dists <- unique(v$district)[1:100]

#model_list_object %>% 
#  filter(district %in% dists)


#work in progress. It looks like the data is not set-up correctly. Might need to pivot wider to make student groups their own individual columns. 
head(combined_clean)

combined_clean %>%
  filter(`District` == "Adrian SD 61") %>%
  ggplot(aes(n, `Academic Year`)) +
  geom_errorbar(mapping = aes(x = `Academic Year`, ymin = 0.3, ymax = -0.1))

````

## Task 4

Save the plots into a “plots” directory. Make sure the file names are meaningful.

``` {r Save_to_dir}


```





