---
title: "FP_midterm"
Author: "Janette Avelar David Fainstein Joe Swinehart Makayla Whitney"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
#Note: see DA's guidance on caching and clearing the cache as needed. If you run into trouble, clear the Knitr cache from the "Knit" menu above.
```

# Part A
## Task 1
Use the given function to download all of the data from the 2014-15 to 2017-18 school years and bind it into a single data frame, using a single function (i.e., one line of code). Note, this may take a minute or two to run, depending on your Internet speed.

Conduct some basic data cleaning to make your data file look like the following.

* Filter for only student groups coded as "White" or "Hispanic/Latino".
* Select variables related to the number of students in each of the levels (1:4), and not percentages or collapsed levels.
* Remove any row that has missing data in any of the n variables

```{r importing_cleaning}
library(purrr)
library(readr)
library(fs)
library(tidyverse)
library(gapr)
library(ggplot2)
library(glue)

#code from DA
download_file <- function(year) {
  link <- glue::glue("https://www.oregon.gov/ode/educator-resources/assessment/TestResults20{year}/pagr_schools_ela_raceethnicity_{year-1}{year}.xlsx")
  rio::import(link, setclass = "tibble", na = c("-", "--", "*"))
}

#Single-line read-in & staple together data frames
combined <- map_dfr(15:18, ~download_file(.), .id = "file")

#Tidy up combined data frame: focus on number of students, exclude percentages and drop NAs
combined_clean <- combined %>% 
  filter(`Student Group` == "White" | `Student Group` == "Hispanic/Latino") %>% 
  select(`Academic Year`,
         `District`,
         `School`,
         `Student Group`,
         `Grade Level`,
         `Number Level 1`,
         `Number Level 2`,
         `Number Level 3`,
         `Number Level 4`) %>% 
  pivot_longer(cols = starts_with("Number"),
               names_to = "level",
               values_to = "n") %>% 
  mutate(level = gsub("Number Level", "", level)) %>% 
  drop_na()
```

## Task 2

Sum the n across grades and school for each district within each academic year, student group, and level. Calculate the number of schools (unique schools listed) for each district. Also move your data to a wider format where the student groups become new columns, filled by the district n. Remove districts that did not report numbers for one or both student groups (i.e., drop missing data from the new columns).

```{r summing_calculating}
  sum_grouped <- combined_clean %>% 
  group_by(`District`) %>% 
  mutate(n_schools = length(unique(`School`))) %>% 
  group_by(`Academic Year`, `District`, `Student Group`, `level`, `n_schools`) %>% 
  summarise(n = sum(n)) %>% 
  pivot_wider(names_from = `Student Group`,
              values_from = "n") %>% 
  drop_na()

sum_grouped_arranged <- sum_grouped [, c(1, 2, 4, 3, 5, 6)]
arrange(sum_grouped_arranged, `District`)
```

# Part 2
## Task 1

Estimate the average achievement differences in terms of an effect size for every school district in the state that reported data on both student groups (i.e., using the data we created above), for each academic year. Conduct this analysis twice, once using group_by() %>% nest() map() and once using nest_by() %>% summarize().

``` {r estimating average diffs}
#ignore the below. This was to raise the API limit
#remotes::install_github("datalorax/gapr")
#remotes::install_github("dpc10ster/RJafroc@662c4bf3bcd725d8fa148a3e7db69168294ae57e")
#Sys.setenv(R_REMOTES_NO_ERRORS_FROM_WARNINGS="true")
#writeLines('PATH="${RTOOLS40_HOME}\\usr\\bin;${PATH}"', con = "~/.Renviron")
#install.packages("remote")
#usethis::create_github_token()
#usethis::edit_r_environ()

# Analysis 1
est1 <- sum_grouped_arranged %>% 
  group_by(`Academic Year`, `District`) %>% 
  nest() %>% 
  mutate(models = map(data, estimate_v, "White", "Hispanic/Latino"))

# Analysis 2
est2 <- sum_grouped_arranged %>% 
  ungroup() %>% 
  nest_by(`Academic Year`, `District`) %>% 
  summarize(estimate_v(.data$data, "White", "Hispanic/Latino"))
```

## Task 2

Reproduce the following plot to confirm that the estimates are equivalent across methods
``` {r reproduce_plot}
# unnest models from est1
est1_models <- est1 %>% 
  unnest(col = c(data)) %>% 
  select(models) %>% 
  unnest(models) %>% 
  unique()

# differentiate est 1 from est2
colnames(est2)[colnames(est2) %in% c("auc", "v", "v_se")] <-c("auc_2", "v_2", "v_se_2")

# stick together
est1_2 <- left_join(est1_models, est2)

# plot
estimate_equiv <- est1_2 %>% 
  ggplot(aes(v, v_2)) +
  geom_point() +
  geom_smooth() +
  theme(axis.title.x = "Estimates with nest()",
        axis.title.y = "Estimates with unnest()") +
  theme_minimal()

estimate_equiv

````

## Task 3

The plot below shows the achievement difference estimates for one school district across years. Produce a similar plot to the below for each of the first 100 school districts. Once you’ve created all the plots, reproduce them again using an alternative method. Make sure you don’t miss the caption noting the number of schools in the district.

``` {r another_plot_production}
#dists <- unique(v$district)[1:100]

#model_list_object %>% 
#  filter(district %in% dists)


#work in progress. It looks like the data is not set-up correctly. Might need to pivot wider to make student groups their own individual columns. 
# head(combined_clean)

# combined_clean %>%
#   filter(`District` == "Bandon SD 54") %>%
#   ggplot(aes(n, `Academic Year`)) +
#   geom_errorbar(mapping = aes(x = `Academic Year`, ymin = 0.3, ymax = -0.1))

# Trying to build from Bandon example in assignment
# We attempted to plot using the 3 values as a single value for geom_point and 2 values for the min/max of error bar but that didn't reflect the plot in the assignment, so again, lost in conceptualizing what we're doing with models and how to plot them
gap_est <- est2 %>% 
  filter(`District` == "Bandon SD 54") %>% 
  ggplot(aes(`Academic Year`, v_2)) +
  #error bars below are specific to Bandon SD 54, where I pulled the 7th element from est2 dataframe. I think we can use a similar approach to average the v_se_2 values across the first 100 schools
  geom_errorbar(mapping = aes(ymin = (v_2 - est2$v_se_2[7]), ymax = (v_2 + est2$v_se_2[7]))) +
  geom_point(aes(`Academic Year`, v_2))

gap_est

# list of 100 unique districts

# Janette's attempt:
# First 100 unique districts:
dists <- unique(est2$`District`)[1:100]
# Next, a single example, simplified:
est2 %>% 
  filter(`District` == "Bandon SD 54") %>% 
  ggplot(., aes(x = `Academic Year`, y = v_2)) +
      geom_errorbar(mapping = aes(ymin = (v_2 - v_se_2), ymax = (v_2 + v_se_2))) +
      geom_point(aes(`Academic Year`, v_2)) +
      guides(fill = "none") +
      labs(title = "Achievement Gap Estimates:",
           x = "School Year",
           y = "Average achievement difference (SD units)")
# Now all plots:
plots <- est1 %>%
  ungroup() %>% 
  # nest_by(`District`) %>% #using nest_by() instead of nest() b/c I think we need rowwise function
  filter(`District` %in% dists) %>% 
  mutate(plots = map2(models, `District`, ~{ #.$data is a potential area that's throwing an error
    ggplot(.x, aes(`Academic Year`, v)) +
      geom_errorbar(mapping = aes(ymin = (v - v_se), ymax = (v + v_se))) + #Trying to generalize from ex.
      geom_point(aes(`Academic Year`, v)) +
      guides(fill = "none") +
      labs(title = glue("Achievement Gap Estimates: {.y}"),
           x = "School Year",
           y = "Average achievement difference (SD units)")
    })
) # ERROR: "plots" must be size 1, not 100
# Is it saying this is trying to create 100 plots for each of the 100 rows?
# If so, no idea.
# If not, no idea.
#To pull up a plot:
plots$plots[[1]]


# Here's the code that was in when I started:
map(est2, ~{
    ggplot(aes(`Academic Year`, v_2)) +
      geom_errorbar(mapping = aes(ymin = (v_2 - est2$v_se_2[.x]), ymax = (v_2 +   
                    est2$v_se_2[.x]))) +
      geom_point(aes(`Academic Year`, v_2))
      scale_fill_distiller(type = "seq",
                           limits = c(0, max(est1$n)),
                           palette = "BuPu",
                           direction = 1) +
      scale_x_continuous(limits = c(0, max(est1$n)),
                         expand = c(0,0)) +
      guides(fill = "none") +
      labs(title = glue("Achievement Gap Estimates: {District}"),
           x = "School Year",
           y = "Average achievement difference (SD units)"
      )}))
````

## Task 4

Save the plots into a “plots” directory. Make sure the file names are meaningful.

``` {r Save_to_dir}
ggplot()

```





