---
title: "FP_midterm"
Author: "Janette Avelar David Fainstein Joe Swinehart Makayla Whitney"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Note: see DA's guidance on caching and clearing the cache as needed.
```

# Part A
## Task 1
Use the given function to download all of the data from the 2014-15 to 2017-18 school years and bind it into a single data frame, using a single function (i.e., one line of code). Note, this may take a minute or two to run, depending on your Internet speed.

Conduct some basic data cleaning to make your data file look like the following.

* Filter for only student groups coded as "White" or "Hispanic/Latino".
* Select variables related to the number of students in each of the levels (1:4), and not percentages or collapsed levels.
* Remove any row that has missing data in any of the n variables

```{r importing_cleaning}
library(purrr)
library(readr)
library(fs)
library(tidyverse)

#code from DA
download_file <- function(year) {
  link <- glue::glue("https://www.oregon.gov/ode/educator-resources/assessment/TestResults20{year}/pagr_schools_ela_raceethnicity_{year-1}{year}.xlsx")
  rio::import(link, setclass = "tibble", na = c("-", "--", "*"))
}

#Single-line read-in & staple together data frames
combined <- map_dfr(15:18, ~download_file(.), .id = "file")

#Tidy up combined data frame: focus on number of students, exlude percentages and drop NAs
combined_clean <- combined %>% 
  filter(`Student Group` == "White" | `Student Group` == "Hispanic/Latino") %>% 
  select(`Academic Year`,
         `District`,
         `School`,
         `Student Group`,
         `Grade Level`,
         `Number Level 1`,
         `Number Level 2`,
         `Number Level 3`,
         `Number Level 4`) %>% 
  pivot_longer(cols = starts_with("Number"),
               names_to = "level",
               values_to = "n") %>% 
  mutate(level = gsub("Number Level", "", level)) %>% 
  drop_na()

```

## Task 2

Sum the n across grades and school for each district within each academic year, student group, and level. Calculate the number of schools (unique schools listed) for each district. Also move your data to a wider format where the student groups become new columns, filled by the district n. Remove districts that did not report numbers for one or both student groups (i.e., drop missing data from the new columns).

```{r summing_calculating}
# David will try this section too - kind of a natural follow up to Part 1

sum_grouped <- combined_clean %>% 
  group_by(`School ID`) %>% 
  
  


```

# Part 2
## Task 1

Estimate the average achievement differences in terms of an effect size for every school district in the state that reported data on both student groups (i.e., using the data we created above), for each academic year. Conduct this analysis twice, once using group_by() %>% nest() map() and once using nest_by() %>% summarize().

``` {r estimating average diffs}

# remotes::install_github("datalorax/gapr")

library(gapr)
d[1:4, ] %>% # data source - just first four rows for first district
  estimate_v("white", "hispanic_latino") # columns for reference/focal groups

```

## Task 2

Reproduce the following plot to confirm that the estimates are equivalent across methods
``` {r reproduce_plot}

````

## Task 3

The plot below shows the achievement difference estimates for one school district across years. Produce a similar plot to the below for each of the first 100 school districts. Once you’ve created all the plots, reproduce them again using an alternative method. Make sure you don’t miss the caption noting the number of schools in the district.

``` {r another_plot_production}
dists <- unique(v$district)[1:100]

model_list_object %>% 
  filter(district %in% dists)

````




